The risk assessment module analyzes a number of different risks that both the team as well as the operator (user of the software) must be aware of during development and use of the software. Each risk is analyzed by multiplying its likelihood of occurring by the impact of the consequences on the group/user. This allows (low-likelihood, high impact) risks to be compared to (high-likelihood, low impact) risks. Most importantly, the last column of the table indicates how the risk can be avoided altogether, so this table should be referenced regularly.

\begin{tabular}{lllllllll}
\hline
ID   & Description                                                                & \begin{tabular}[c]{@{}l@{}}Likelihood\\        \%\end{tabular} & \begin{tabular}[c]{@{}l@{}}Impact\\  1 - 10\end{tabular} & \begin{tabular}[c]{@{}l@{}}Exposure\\     L * I\end{tabular} & Owner               & Consequences                                                                                 & \begin{tabular}[c]{@{}l@{}}Justification\\ of likelihood\\ percentages\end{tabular}                                                                                                                                                                                    & Prevention                                                                                       \\
R-01 & Team Conflict                                                              & 10\%                                                           & 1                                                        & 0.1                                                          & Team                & Reduced Productivity                                                                         & Team has rules in place to avoid conflict.                                                                                                                                                                                                                             & Don’t be mean, rude, etc                                                                         \\
R-02 & Unfamiliar Development Tools                                               & 20\%                                                           & 2                                                        & 0.4                                                          & Team                & Reduced Productivity as time spent learning how to use dev tools                             & Members of the team have all been learning how to use the same development tools.                                                                                                                                                                                      & Use Dev Tools that majority are familiar with / easy to learn                                    \\
R-03 & Unfamiliar APIs/ libraries, various programming skill levels               & 90\%                                                           & 5                                                        & 4.5                                                          & Team                & Some members limited to certain tasks, may mean some membes have to do more work than others & This is the team's first project of this scale. Therefore there are many different API’s and libraries that members of the team are not familiar with.                                                                                                                 & Discuss what libraries may be used                                                               \\
R-04 & Miscommunication with lecturers                                            & 80\%                                                           & 5                                                        & 4                                                            & Team                & Doing tasks incorrectly and will have to redo or get a bad mark                              & The team has very little contact time with the lecture team. Therefore it is easy for a team member to hear and implement something different to what the lecturer was trying to say.                                                                                  & Make sure all team members attend lectures and labs                                              \\
R-05 & Loss of data, problem with import of data                                  & 20\%                                                           & 6                                                        & 1.2                                                          & Team                & Have to re-complete work / manually import                                                   & All members of the team are familiar with Git, which will be used for version control.                                                                                                                                                                                 & Make sure dev tools are compatible with each other                                               \\
R-06 & Product does not agree with stakeholders expectations                      & 90\%                                                           & 10                                                       & 9                                                            & Team / Stakeholders & Software won’t sell (fake world) / bad mark from lecturers (real world)                      & It is very unlikely that the system will be able to be built to the stakeholders exact specifications and therefore constant communication between the team and the stakeholders is required to find some middle ground between what is possible and what is expected. & Make sure we have a balance of focussing on what the lecturers want compared to our stakeholders \\
R-07 & Code written by individual team members not readable by others             & 70\%                                                           & 4                                                        & 2.8                                                          & Team                & Reduced Productivity / Code has to be re-written                                             & With new tools being used to create this system it is very likely that one team member does a lot of research in order to write a piece of code that cannot be understood by other team members.                                                                       & Document and comment code to make it more readable / use good variable names                     \\
R-08 & GitLab, Google Drive, etc. become unavailable                              & 2\%                                                            & 7                                                        & 0.14                                                         & Team                & Reduced Productivity, Can’t commit new changes, may have to switch platforms                 & These services are run by large companies and it is very unlikely for them to become unavailable.                                                                                                                                                                      & Keep a running offline backup of the project                                                     \\
R-09 & No Internet                                                                & 5\%                                                            & 6                                                        & 0.3                                                          & Team                & Can’t commit changes to GitLab                                                               & Internet is provided at many public places. It is very unlikely that no internet is available.                                                                                                                                                                         & Come to Uni if you don’t have access to internet                                                 \\
R-10 & Bug in software e.g. bug says something gluten free when actually it isn’t & 90\%                                                           & 10                                                       & 9                                                            & Team                & People could get sick                                                                        & It is very unlikely that there will be no bugs during development. These bugs will need to be found and fixed before deployment.                                                                                                                                       & Can be prevented with good UUID system
\end{tabular}